### 2015-02-17 src/4_OnlineLearning.tex
Inicio capitulo ML

\chapter{Machine Learning Models}
\section{Batch learning}
\section{Online learning}
\subsection{Online learning}

>>>>

\chapter{Machine Learning Models}
Machine learning is a scientific discipline focused on the development of algorithms focused on learning from examples. This idea has become central to the design of search engines, robots systems and forecasts applications which process large data sets. However, machines require an extended training period when developing algorithms to predict future behaviour such as financial time series forecasting where new data is available in a short period of time.  Online machine learning techniques tackle this problems and allow to update the model with new data or to compute a new model using less data and in a short period of time.

\vspace{0.5cm}

\section{Introduction}

There are three types of Machine Learning (ML) classified depending on the nature of the learning input or output available to a learning system.
\begin{description}
\item[supervised learning] also known as classification or regression \cite{bishop2006}, the input data  is a pair which contains the example input and its desired outputs (also called labels). The goal is to learn a general rule that maps inputs to outputs.
 Its two mainstream approaches are: support vector machines (SVMs) \cite{vapnik1998} and ensemble learning \cite{breiman1998}.
\item[unsupervised learning] also known as clustering \cite{ben2005} and reinforcement learning \cite{sutton1998}.
\end{description}

All three types of problems can be viewed as optimization problems. The ML core task is to define a learning criterion, i.e the function to be optimized.

\section{Batch learning}
\section{Online learning}
\subsection{Online learning}
